### 2021-01-06 paper/natastron/2nd_draft/paper.tex
updated to Qwmb fully now

Both hot and sub-giant stars do not strongly prefer one model over the other (with both cumulative probabilities crossing the $Q_{\rm{WMB}} = 0.5$ line at roughly $45\%$), which is expected given that these stars in our sample all lie at hot temperatures near the Kraft break. When performing this analysis on all 89 stars for which seismic rotation was measured (excluding the two stars with low metallicity), the total probability above $Q_{\rm{WMB}} = 0.5$ is 96.6\%. \\

>>>>

Both hot and sub-giant stars do not strongly prefer one model over the other (with both cumulative probabilities crossing the $Q_{\rm{WMB}} = 0.5$ line at roughly $60\%$), which is expected given that these stars in our sample all lie at hot temperatures near the Kraft break. When performing this analysis on all 89 stars for which seismic rotation was measured (excluding the two stars with low metallicity), the total probability above $Q_{\rm{WMB}} = 0.5$ is 96.6\%. \\
